---
title: "mtcars Data"
author: "Abdalrhman Hassan"
date: "January 23, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Preface

** mtcars Data **
This project shows the data and the code that has been used in the shiny project.

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).
Also, the data has 32 obsarvatio and 11 variable:

Index	  Field	    Detail
[, 1]	   mpg	    Miles/(US) gallon

[, 2]	   cyl	    Number of cylinders

[, 3]	   disp	    Displacement (cu.in.)

[, 4]	   hp	      Gross horsepower

[, 5]	   drat	    Rear axle ratio

[, 6]	   wt	      Weight (lb/1000)

[, 7]	   qsec	    1/4 mile time

## preface

[, 8]	   vs	      V/S

[, 9]	   am	      Transmission (0 = automatic, 1 = manual)

[,10]	   gear	    Number of forward gears

[,11]	   carb	    Number of carburetors


## mtcars dataset

```{r cars, echo = TRUE}
head(mtcars)
```

## The code


mtcars$am <- factor(mtcars$am, labels = c("Automatic", "Manual"))

shinyServer(function(input, output) {
  
  formulaText <- reactive({
    paste("mpg ~", input$variable)
  })
  
  formulaTextPoint <- reactive({
    paste("mpg ~", "as.integer(", input$variable, ")")
  })
  
  fit <- reactive({
    lm(as.formula(formulaTextPoint()), data=mtcars)
  })
  
  output$caption <- renderText({
    formulaText()
  })
  
  
## The Code 
  
  output$mpgBoxPlot <- renderPlot({
    boxplot(as.formula(formulaText()), 
            data = mtcars,
            outline = input$outliers)
  })
  
  output$fit <- renderPrint({
    summary(fit())
  })
  
  output$mpgPlot <- renderPlot({
    with(mtcars, {
      plot(as.formula(formulaTextPoint()))
      abline(fit(), col=2)
    })
  })
  
})


